surface-flask

### 2024-08-26 examples/README_nc.Rmd
add surface-flask examples and articles

To maintain a coherent approach among text and NetCDF files, 
we will add a column altitude_final and type_altitude

```{r}
df$altitude_final <- df$intake_height
df$type_altitude <- ifelse(df$dataset_intake_ht_unit == "magl", 0, 1)
```

@@

```{r}
df2 <- obs_addtime(df)
```
Then we need a *key_time* to aggregate data.
This can be done using UTC, solar, or local time.
The normal approach is using afternoon solar or local time.

>>>>

To maintain a coherent approach among text and NetCDF files, 
we will add a column altitude_final and type_altitude. This
is done in `obs_read_nc` or `obs_read`.

@@

```{r}
df2 <- obs_addtime(df)
```

Then we need a *key_time* to aggregate data.
This can be done using UTC, solar, or local time.
The normal approach is using afternoon solar or local time.

### 2024-08-26 examples/surface-flask.Rmd
add surface-flask examples and articles

---
title: "surface-insitu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{surface-insitu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

cate = c("aircraft-pfp",
         "aircraft-insitu",
         "aircraft-flask",
         "surface-insitu",
         "surface-flask", 
         "surface-pfp",   
         "tower-insitu",  
         "aircore",       
         "shipboard-insitu",
         "shipboard-flask")

@@

Now we read the surface-insitu using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.

```{r readnc, eval = T}
datasetid <- "surface-insitu"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_surfaceinsitu.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfacetinsitu.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_surfaceinsitu_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfaceinsitu_map.png?raw=true)

>>>>

---
title: "surface-flask"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{surface-flask}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

cate = c("aircraft-pfp",
         "aircraft-flask",
         "aircraft-flask",
         "surface-flask",
         "surface-flask", 
         "surface-pfp",   
         "tower-flask",  
         "aircore",       
         "shipboard-flask",
         "shipboard-flask")

@@

Now we read the surface-flask using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.

```{r readnc, eval = T}
datasetid <- "surface-flask"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_surfaceflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfacetflask.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_surfaceflask_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfaceflask_map.png?raw=true)
